Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-06-14 PAPER.tex
added transition back to FRF toy model

While the connection between the rate of convergence of an empirical eigenvector with the steepness of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss. In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode. Even for the case of real PAPER data (Section \ref{sec:Sigloss}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds. However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between eigenmodes that determines how quickly they converge, and hence how much signal loss can result.\cc{end of carina edits}

@@

The power spectrum results for the fringe-rate filtered toy model data are shown in Figure \ref{fig:toy_sigloss7}. As 
expected, there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance. In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter. This is evident by noticing that the 
green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum.

>>>>

While the connection between the rate of convergence of an empirical eigenvector with the steepness of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss. In the toy models throughout Section \ref{sec:SiglossOverview}, we exploit the fact that the strongest eigenmode (highest eigenvalue mode) is dominated by foregrounds in order to purposely incur signal loss for that mode. Even for the case of real PAPER data (Section \ref{sec:Sigloss}), we make the assumption that the strongest eigenmodes are likely the most contaminated by foregrounds. However, in general, foregrounds need not be restricted to the strongest eigenmodes, and as we have seen, it is really the degeneracies between eigenmodes that determines how quickly they converge, and hence how much signal loss can result.

@@

With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our fringe-rate filtered toy model. \cc{end of carina edits}The power spectrum results for this model are shown in Figure \ref{fig:toy_sigloss7}, and as 
expected there is a much larger amount of signal loss for this time-averaged dataset since we do a worse job estimating the true covariance. In addition, as a result of having fewer independent samples, we obtain an estimate with more scatter. This is evident by noticing that the 
green curve in Figure \ref{fig:toy_sigloss7} fails to trace the shape of the uniform-weighted EoR power spectrum.
